### 2025-06-20 simulation.qmd
20250619 - update monte carlo simulation

```{r}
monteCarloSim_results <- monteCarloSim_results %>% 
  left_join(
    nfl_playerIDs[,c("mfl_id","name","merge_name","position","team")],
    by = c("id" = "mfl_id")
  ) %>% 
  select(name, team, position, everything()) %>% 
  arrange(-mean_pts_mean)
```

>>>>

monteCarloSim_results <- monteCarloSim_results %>% 
  left_join(
    nfl_playerIDs[,c("mfl_id","name","merge_name","position","team")],
    by = c("id" = "mfl_id")
  ) %>% 
  select(name, team, position, everything()) %>% 
  arrange(-mean_pts_mean)
```
